6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-01-18 paper.tex
Tweak thesis title

\section{Thesis}
\textit{It is practical and useful to develop an infrastructure modelling and monitoring tool to help address inherent complexity in modern IT infrastructure.}
\section{Motivation}

>>>>

\section{Thesis}
\textit{It is practical and useful to develop an infrastructure modelling and monitoring tool to help address the inherent complexity in modern IT infrastructure.}
\section{Motivation}
